Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-05-16 cordillera-cycle.tex
Throw some ideas on figure improvement.
Add Irina's corrections in abstract.

% My commands
\def\todo#1{\textcolor[rgb]{0.5,0,0}{\textbf{[TODO: #1]}}}
\def\aref{\textcolor[rgb]{0.5,0,0}{\textbf{[REF]}}}

@@

  Despite more than a century of geological observations, the Cordilleran ice
  sheet of North America remains poorly understood in terms of its former
  extent, volume and dynamics. Although geomorphological evidence is abundant,
  its complexity is such that whole ice-sheet reconstructions of advance and
  retreat patterns are lacking. Here we use a numerical ice sheet model
  calibrated by field-based evidence to attempt a quantitative reconstruction
  of Cordilleran ice sheet history through the last glacial cycle. Surface mass
  balance is computed by a positive degree-day model forced by time-dependent
  temperature offsets from six proxy records located around the globe. Although
  this approach reveals large variations in model response to atmospheric
  forcing, all simulations produce two major glaciations events during MIS~4
  (60\,\unit{kyr}) and MIS~2 (20\,\unit{kyr}). The timing of glaciation is
  better reproduced using temperature forcing derived from Greenland and
  Antarctic ice-core than from regional ocean sediment cores. During most of
  the last glacial cycle, the modelled ice cover is discontinuous and
  restricted to high mountain areas. However, widespread precipitation over the
  Skeena mountains favours the persistence of a central ice dome throughout the
  glacial cycle. It acts as a nucleation centre before last glacial maximum
  (35\,\unit{kyr}) and hosts the last remain of Cordilleran ice during the
  early Holocene (8\,\unit{kyr}).

@@

% fig:atm
\begin{figure}
  \includegraphics{atm}
  \caption{Focring climatology. In construction.}
  \label{fig:atm}
\end{figure}

% fig:multirec-timeseries
\begin{figure}
  \includegraphics{multirec-timeseries}
  \caption{Multi-record timeseries. In construction.}
  \label{fig:multirec-timeseries}
\end{figure}

% fig:multirec-snapshots
\begin{figure}
  \includegraphics{multirec-snapshots}
  \caption{Multi-record snapshots. In construction.}
  \label{fig:multirec-snapshots}
\end{figure}

% fig:hires-timeseries
\begin{figure}
  \includegraphics{hires-timeseries}
  \caption{High resolution timeseries. In construction.}
  \label{fig:hires-timeseries}
\end{figure}

% fig:hires-snapshots
\begin{figure}
  \includegraphics{hires-snapshots}
  \caption{High resolution snapshots. In construction.}
  \label{fig:hires-snapshots}
\end{figure}

% fig:duration
\begin{figure}
  \includegraphics{duration}
  \caption{Ice cover duration. In construction.}
  \label{fig:duration}
\end{figure}

% fig:deglac
\begin{figure}
  \includegraphics{deglac}
  \caption{Deglaciation age. In construction.}
  \label{fig:deglac}
\end{figure}

>>>>

% My commands
\def\idea#1{\textcolor[rgb]{0,0.5,0}{\textbf{[IDEA: #1]}}}
\def\todo#1{\textcolor[rgb]{0.5,0,0}{\textbf{[TODO: #1]}}}
\def\aref{\textcolor[rgb]{0.5,0,0}{\textbf{[REF]}}}

@@

  Despite more than a century of geological observations, the Cordilleran ice
  sheet of North America remains poorly understood in terms of its former
  extent, volume and dynamics. Although geomorphological evidence is abundant,
  its complexity is such that whole ice-sheet reconstructions of advance and
  retreat patterns are lacking. Here we use a numerical ice sheet model
  calibrated against field-based evidence to attempt a quantitative
  reconstruction of the Cordilleran ice sheet history through the last glacial
  cycle. A series of simulations is driven by time-dependent temperature
  offsets from six proxy records located around the globe. Although this
  approach reveals large variations in model response to evolving atmospheric
  forcing, all simulations produce two major glaciations events during MIS~4
  (60\,\unit{kyr}) and MIS~2 (20\,\unit{kyr}). The timing of glaciation is
  better reproduced using temperature forcing derived from Greenland and
  Antarctic ice-core than from regional ocean sediment cores. During most of
  the last glacial cycle, the modelled ice cover is discontinuous and
  restricted to high mountain areas. However, widespread precipitation over the
  Skeena mountains favours the persistence of a central ice dome throughout the
  glacial cycle. It acts as a nucleation centre before the last glacial maximum
  (35\,\unit{kyr}) and hosts the last remain of Cordilleran ice during the
  early Holocene (8\,\unit{kyr}).

@@

% fig:atm
\begin{figure}
  \includegraphics{atm}
  \caption{Focring climatology. In construction.
           \idea{Show seasonal variability}}
  \label{fig:atm}
\end{figure}

% fig:multirec-timeseries
\begin{figure}
  \includegraphics{multirec-timeseries}
  \caption{Multi-record timeseries. In construction.
           \todo{Add NGRIP}
           \idea{Use same colors but different patterns for similar records}}
  \label{fig:multirec-timeseries}
\end{figure}

% fig:multirec-snapshots
\begin{figure}
  \includegraphics{multirec-snapshots}
  \caption{Multi-record snapshots. In construction.
           \todo{Add NGRIP}}
  \label{fig:multirec-snapshots}
\end{figure}

% fig:hires-timeseries
\begin{figure}
  \includegraphics{hires-timeseries}
  \caption{High resolution timeseries. In construction.
           \todo{Use same scaling at low and high resolution}
           \idea{Compare to low-resolution}}
  \label{fig:hires-timeseries}
\end{figure}

% fig:hires-snapshots
\begin{figure}
  \includegraphics{hires-snapshots}
  \caption{High resolution snapshots. In construction.
           \idea{Fewer snapshots, bigger figure}}
  \label{fig:hires-snapshots}
\end{figure}

% fig:duration
\begin{figure}
  \includegraphics{duration}
  \caption{Ice cover duration. In construction.
           \todo{Add Antarctic-record high-resolution simulation}}
  \label{fig:duration}
\end{figure}

% fig:deglac
\begin{figure}
  \includegraphics{deglac}
  \caption{Deglaciation age. In construction.
           \todo{Add Antarctic-record high-resolution simulation}
           \idea{Compare to Dyke deglaciation outlines}}
  \label{fig:deglac}
\end{figure}
